Phenology and Mycorrhizae Manuscript

### 2023-01-10 DataExploratoryAnalyses.Rmd
Downloading more NEON data

```{r}
p <- 2 #Bud burst 
  print(NEON_phenophase_names[p])
  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
  subDat <- subDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p],
                              growthForm=="Deciduous broadleaf")
  subDat$year <- as.numeric(subDat$year)

@@

#Is phenology correlated with soil microbial biodiversity? 
```{r}
allBioDat <- read.csv(paste0(dataPath,dataName,"/soilMicrobediversityData.csv"))

@@

allPCdat_cleaned_15 <- allPCdat_cleaned %>% filter(direction=="rising",transition==15,veg_type=="DB")

allBioDat_plotFiltered_15 <- left_join(allBioDat_plotFiltered,allPCdat_cleaned_15,by=c('year','siteID'))

plot(allBioDat_plotFiltered_15$biodiversity,allBioDat_plotFiltered_15$GDD_0,pch=20)
mdl <- lm(GDD_0~biodiversity,data = allBioDat_plotFiltered_15)
abline(mdl)
summary(mdl)

>>>>

```{r,eval=FALSE}
p <- 2 #Bud burst 
  print(NEON_phenophase_names[p])
  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
  subDat <- subDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p],
                              growthForm=="Deciduous broadleaf")
  subDat$year <- as.numeric(subDat$year)

@@

#Is phenology correlated with soil microbial biodiversity? 
```{r}
dataName <- "NEON_SoilMicrobeComposition"
allBioDat <- read.csv(paste0(dataPath,dataName,"/soilMicrobediversityData.csv"))

@@

transitions <- c(15,50,85)
t=1

par(mfrow=c(2,3))
for(drt in c("rising","falling")){
  for(t in seq_along(transitions)){
    allPCdat_cleaned_trans <- allPCdat_cleaned %>% 
      filter(direction==drt,transition==transitions[t],veg_type=="DB")
    allBioDat_plotFiltered_trans <- left_join(allBioDat_plotFiltered,allPCdat_cleaned_trans,by=c('year','siteID'))

    mdl <- lm(GDD_5~biodiversity,data = allBioDat_plotFiltered_trans)
    sm <- summary(mdl)
    plot(allBioDat_plotFiltered_trans$biodiversity,allBioDat_plotFiltered_trans$GDD_5,pch=20,
         ylab="Biodiversity",xlab=paste0("GDD_5 at ",transitions[t],"% ",drt),main=paste("p-value on slope:",round(sm$coefficients[2,4],digits=3)))

    abline(mdl)
    summary(mdl)
  }
}

par(mfrow=c(1,1))
```

### 2023-01-10 manuscriptCode_phenologyAndMycorrhizae.Rmd
Downloading more NEON data

#Download NEON Soil Microbe Data
```{r}
dataName="NEON_SoilMicrobeComposition"
NEON_ID='DP1.10081.001'
selectColumns <-
inFileName <- c("mcc_soilSeqVariantMetadata_16S.csv","mcc_soilSeqVariantMetadata_ITS.csv")
varName <-

@@

>>>>

#Download NEON Soil Microbe Data
```{r}
dataName="NEON_SoilMicrobeComposition"
NEON_ID='DP1.10081.001'
#selectColumns <-
inFileName <- c("mcc_soilSeqVariantMetadata_16S.csv","mcc_soilSeqVariantMetadata_ITS.csv")
#varName <-

@@

#Download NEON Soil Physical and Chemical Properties
```{r}
dataName <- "NEON_soilProperties"
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}
NEON_ID <- "DP1.10086.001"
downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
#inFileNames <- c(,"sls_soilMoisture","sls_soilpH")
inFileName <- "sls_soilCoreCollection.csv"
selectColumns <- c('plotID','decimalLatitude','decimalLongitude','elevation','standingWaterDepth','horizon',
                   'soilTemp','litterDepth','sampleTopDepth','sampleBottomDepth')
dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)

inFileName <- "sls_soilpH.csv"
selectColumns <- c('plotID','horizon','soilInWaterpH','soilInCaClpH','pHSoilInWaterMass','pHWaterVol',
                   'waterpHRatio','pHSoilInCaClMass','pHCaClVol','caclpHRatio')
dat2 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
allDat <- full_join(dat1,dat2,by=c('siteID','collectDate','plotID','horizon'))

inFileName <- "sls_soilMoisture.csv"
selectColumns <- c('plotID','horizon','boatMass','freshMassBoatMass','dryMassBoatMass','soilMoisture','dryMassFraction')
dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
allDat <- full_join(allDat,dat3,by=c('siteID','collectDate','plotID','horizon'))

outFileName <- paste0(dataName,"ALLdata.csv")
write.csv(file=paste0(dataPath,outFileName),allData,row.names = FALSE,quote=FALSE)

#Download Photosynthetically active radiation (PAR)
```{r}
dataName="NEON_PAR"
NEON_ID='DP1.00024.001'
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}
# selectColumns <- c('precipBulk','precipExpUncert','precipQF')
# inFileName <- c("PRIPRE_30min.csv","SECPRE_30min.csv")
# varName <- "precipBulk"
